Scipion Tailored for TEM Facilities: Image Processing in Streaming

### 2018-02-27 3.workflow_scilifelab.tex
A bit more on SciLifeLab intro

>>>>

At the beginning of 2016, the Cryo-EM facility at SciLifeLab became one of the early adopters of Scipion 
for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncor)
and CTF estimation (with Gctf). The microscope operators recognized the importance of  
a more general framework with the possibility to be extended with new programs. Another strong point was the 
the availability of graphical tools for data analysis and quick feedback about the data collection. Initially, the 
same setup script from the CNB was used, but it has some limitations for this more complex setup with more 
requirements. In the following sections we will briefly describe the computational infrastructure at the
SciLifeLab node and the implementation of a Session Wizard to automate the initial setup while fetching 
information from other sources external to Scipion.

\subsubsection{Infrastructure}

\subsubsection{Session Wizard}
